### 2022-01-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@0688247d1354ca4f0fd4214e851dd5f46c103a9e 🚀

Having a general solution for inferring \emph{potential} interactions
(despite the unavailability of interaction data) could be the catalyst
for significant breakthroughs in our ability to start thinking about
species interaction networks over large spatial scales (Hortal et al.,
2015). In a recent overview of the field of ecological network
prediction, Strydom, Catchen, et al. (2021) identified two challenges of
interest to the prediction of interactions at large scales. First, there
is a relative scarcity of relevant data in most places globally --
paradoxically, this restricts our ability to infer interactions to
locations where inference is perhaps the least required; second,
accurate predictions often demand accurate predictors, and the lack of
methods that can leverage small amount of data is a serious impediment
to our predictive ability globally.

Following the definition of Dunne (2006), a metaweb is a network
analogue to the regional species pool; specifically, it is an inventory
of all \emph{potential} interactions between species from a spatially
delimited area (and so captures the \(\gamma\) diversity of
interactions). The metaweb is, therefore, \emph{not} a prediction of the
food web at a specific locale within the spatial area it covers, and
will have a different structure (notably by having a larger connectance;
see \emph{e.g.} Wood et al., 2015). These local food webs (which
captures the \(\alpha\) diversity of interactions) are a subset of the
metaweb's species and interactions, and have been called ``metaweb
realizations'' (Poisot et al., 2015). Differences between local food web
and their metaweb are due to chance, species abundance and
co-occurrence, local environmental conditions, and local distribution of
functional traits, among others.

Because the metaweb represents the joint effect of functional,
phylogenetic, and macroecological processes (Morales-Castilla et al.,
2015), it holds valuable ecological information. Specifically, it is the
``upper bounds'' on what the composition of the local networks can be
(see \emph{e.g.} McLeod et al., 2021). These local networks, in turn,
can be reconstructed given appropriate knowledge of local species
composition, providing information on structure of food webs at finer
spatial scales. This has been done for example for
tree-galler-parasitoid systems (Gravel et al., 2018), fish trophic
interactions (Albouy et al., 2019), tetrapod trophic interactions
(O'Connor et al., 2020), and crop-pest networks (Grünig et al., 2020).
Whereas the original metaweb definition, and indeed most past uses of
metawebs, was based on the presence/absence of interactions, we focus on
\emph{probabilistic} metawebs where interactions are represented as the
chance of success of a Bernoulli trial (see \emph{e.g.} Poisot et al.,
2016); therefore, not only does our method recommend interactions that
may exist, it gives each interaction a score, allowing us to properly
weigh them.

@@

Yet, owing to the inherent plasticity of interactions, there have been
documented instances of food webs undergoing rapid collapse/recovery
cycles over short periods of time (Pedersen et al., 2017). The embedding
of a network, in a sense, embeds its macro-evolutionary history,
especially as RDPG captures ecological signal (Dalla Riva \& Stouffer,
2016); at this point, it is important to recall that a metaweb is
intended as a catalogue of all potential interactions, which should then
be filtered (Morales-Castilla et al., 2015). In practice (and in this
instance) the reconstructed metaweb will predict interactions that are
plausible based on the species' evolutionary history, however some
interactions would/would not be realized due to human impact.

Dallas et al. (2017) suggested that most links in ecological networks
may be cryptic, \emph{i.e.} uncommon or otherwise hard to observe. This
argument essentially echoes Jordano (2016): the sampling of ecological
interactions is difficult because it requires first the joint
observation of two species, and then the observation of their
interaction. In addition, it is generally expected that weak or rare
links would be more common in networks (Csermely, 2004), compared to
strong, persistent links; this is notably the case in food chains,
wherein many weaker links are key to the stability of a system (Neutel
et al., 2002). In the light of these observations, the results in
fig.~\ref{fig:inflation} are not particularly surprising: we expect to
see a surge in these low-probability interactions under a model that has
a good predictive accuracy. Because the predictions we generate are by
design probabilistic, then one can weigh these rare links appropriately.
In a sense, that most ecological interactions are elusive can call for a
slightly different approach to sampling: once the common interactions
are documented, the effort required in documenting each rare interaction
may increase exponentially. Recent proposals suggest that machine
learning algorithms, in these situations, can act as data generators
(Hoffmann et al., 2019): in this perspective, high quality observational
data can be supplemented with synthetic data coming from predictive
models, which increases the volume of information available for
inference. Indeed, Strydom, Catchen, et al. (2021) suggested that
knowing the metaweb may render the prediction of local networks easier,
because it fixes an ``upper bound'' on which interactions can exist;
indeed, with a probabilistic metaweb, we can consider that the metaweb
represents an aggregation of informative priors on the interactions.

@@

>>>>

Being able to infer \emph{potential} interactions could be the catalyst
for significant breakthroughs in our ability to start thinking about
species interaction networks over large spatial scales (Hortal et al.,
2015). In a recent overview of the field of ecological network
prediction, Strydom, Catchen, et al. (2021) identified two challenges of
interest to the prediction of interactions at large scales. First, there
is a relative scarcity of relevant data in most places globally --
paradoxically, this restricts our ability to infer interactions to
locations where inference is perhaps the least required; second,
accurate predictions often demand accurate predictors, and the lack of
methods that can leverage small amount of data is a serious impediment
to our global predictive ability. In most places, our most reliable
biodiversity knowledge is that of a species pool: through the analysis
of databases like GBIF or IUCN, it is possible to establish a list of
species in a region of interest; but establishing the interactions
between these species is difficult.

Following the definition of Dunne (2006), a metaweb is the ecological
network analogue to the species pool; specifically, it iventories
\emph{potential} interactions between species from a spatially delimited
area (and so captures the \(\gamma\) diversity of interactions). The
metaweb is not a prediction of the network at a specific point within
the spatial area it covers: it will have a different structure, notably
by having a larger connectance (see \emph{e.g.} Wood et al., 2015), from
any of these local networks. These local networks (capturing the
\(\alpha\) diversity of interactions) are a subset of the metaweb's
species and interactions, and have been called ``metaweb realizations''
(Poisot et al., 2015). Differences between local networks and their
metawebs are due to chance, species abundance and co-occurrence, local
environmental conditions, and local distribution of functional traits,
among others.

Because the metaweb represents the joint effect of functional,
phylogenetic, and macroecological processes (Morales-Castilla et al.,
2015), it holds valuable ecological information. Specifically, it is the
``upper bounds'' on what the composition of the local networks can be
(see \emph{e.g.} McLeod et al., 2021). These local networks may be
reconstructed given appropriate knowledge of local species composition,
providing information on structure of food webs at finer spatial scales.
This has been done for example for tree-galler-parasitoid systems
(Gravel et al., 2018), fish trophic interactions (Albouy et al., 2019),
tetrapod trophic interactions (O'Connor et al., 2020), and crop-pest
networks (Grünig et al., 2020). In this contribution, we highlight the
\emph{probabilistic} nature of metawebs, discuss how a family of machine
learning tools (graph embeddings and transfer learning) can be used to
overcome data limitations to metaweb inference, and highlight how the
use of metawebs introduces important questions for the field of network
ecology.

@@

Dallas et al. (2017) suggested that most links in ecological networks
are cryptic, \emph{i.e.} uncommon or hard to observe. This argument
echoes Jordano (2016): sampling ecological interactions is difficult
because it requires first the joint observation of two species, and then
the observation of their interaction. In addition, it is generally
expected that weak or rare links would be more common in networks
(Csermely, 2004), compared to strong, persistent links; this is notably
the case in food chains, wherein many weaker links are key to the
stability of a system (Neutel et al., 2002). In the light of these
observations, we expect to see an over-representation of low-probability
interactions under a model that accurately predicts interaction
probabilities. Yet the original metaweb definition, and indeed most past
uses of metawebs, was based on the presence/absence of interactions.
Moving towards \emph{probabilistic} metawebs, by represent interactions
as Bernoulli events (see \emph{e.g.} Poisot et al., 2016), offers the
opportunity to weigh these rare interactions appropriately. The inherent
plasticity of interactions is important to capture: there have been
documented instances of food webs undergoing rapid collapse/recovery
cycles over short periods of time (\emph{e.g.} Pedersen et al., 2017).
These considerations emphasize why metaweb predictions should focus on
quantitative (preferentially probabilistic) predictions; this should
constrain the suite of appropriate models.

Yet it is important to recall that a metaweb is intended as a catalogue
of all potential interactions, which is then filtered (Morales-Castilla
et al., 2015). In a sense, that most ecological interactions are elusive
can call for a slightly different approach to sampling: once the common
interactions are documented, the effort required in documenting each
rare interaction will increase exponentially, and will do so for each
undocumented interaction. Recent proposals suggest that machine learning
algorithms, in these situations, can act as data generators (Hoffmann et
al., 2019): high quality observational data can generate the core rules
underpinning the network structure, and be supplemented with synthetic
data coming from predictive models, increasing the volume of information
available for inference. Indeed, Strydom, Catchen, et al. (2021)
suggested that knowing the metaweb may render the prediction of local
networks easier, because it fixes an ``upper bound'' on which
interactions can exist. A probabilistic metaweb represents an
aggregation of informative priors on the interactions, an elusive
information with the potential to boost our predictive ability
(\textbf{Bartomeus2016ComFra?}).

@@

The embedding of a network, in a sense, embeds its macro-evolutionary
history, especially as RDPG captures ecological signal (Dalla Riva \&
Stouffer, 2016); at this point,
